---
title: "Chemical Conversations: Linguistic Markers of Authenticity and Emotionality Under MDMA Influence"
shorttitle: "Chemical Conversations"
author:
  - name: Deeksha Handa
    corresponding: false
    CNETID: 12459274
    email: handad@uchicago.edu
    affiliations:
      - name: University of Chicago
        department: Social Sciences Department
        city: Chicago
abstract: MDMA (3,4-methylenedioxymethamphetamine) has been widely studied for its potential therapeutic effects, particularly in facilitating emotional openness and enhancing psychotherapy outcomes. Recent research suggests that MDMA alters speech patterns, increasing emotional expressivity and authenticity, which may play a crucial role in therapeutic settings. This study aims to examine the linguistic markers of authenticity, emotionality, and fluency under the influence of MDMA, particularly in the context of familiarity with a conversational partner. Using a secondary analysis of data collected in a controlled clinical setting, this study employs linguistic analysis techniques, including the Linguistic Inquiry and Word Count (LIWC) tool, to quantify changes in speech. Participants engaged in conversations under four conditions—MDMA vs. placebo and familiar vs. unfamiliar partner—to assess the interaction of drug effects and social context. We hypothesize that MDMA will increase authenticity and emotional expression with familiarity further amplifying emotional expressivity. Understanding these linguistic shifts can provide valuable insights into MDMA-assisted therapy (MDMA-AT), informing therapeutic approaches and practitioner training.
keywords: [MDMA, MDMA-AT, linguistic, LIWC]
author-note: |
  This research was conducted as part of the Master of Arts Program in the Social Sciences (MAPSS) at the University of Chicago, under the guidance of faculty advisor Dr. Harriet de Wit and preceptor Dr. Amanda Ceniti. The study utilizes secondary data from a clinical MDMA study performed at the Human Behavioral Pharmacology Lab, with ethical approval granted by the University of Chicago. All participants provided informed consent, and ethical considerations regarding participant safety and confidentiality were strictly followed. 
disclosures:
  conflict-of-interest: "The author has no conflict of interest to declare."
bibliography: "CCbibliography.bib"  # Ensure you have a BibTeX file in your directory
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf: default
---
```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Load necessary packages
library(knitr)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(forcats)
library(citr)
library(nlme)
```
3,4-methylenedioxymethamphetamine (MDMA) is a synthetic drug categorized as both a
stimulant and a psychedelic, with effects comparable to methamphetamines [@_2024_mdma]. It is more commonly known as ecstasy (pill form) and molly (crystal form). After its classification as a Schedule I drug in 1985,unregulated research and any clinical use of MDMA to treat psychological disorders like Post-Traumatic Stress Disorder (PTSD) came to a sudden halt. Initial research and testing from the 1970s had shown MDMA’s potential as a less toxic,legal alternative to MDA (3,4-methylenedioxy-amphetamine) for assisting therapy seekers intheir emotional expression. Its clinical value centered on MDMA’s unique ability to help patients open-up emotionally, encouraging deeper thought and introspection without overwhelming psychedelic hallucinations. Leading therapists and scholars within the field believed that these effects would enable otherwise hard to articulate experiences to become easily expressible in therapeutic settings [@passie_2018_early].

# Recent Clinical Developments and Methodological Challenges
In recent years, however, 11 Phase 2 and two Phase 3 trials of MDMA-Assisted
Therapy (MDMA-AT) for PTSD treatment have been approved and conducted. Notably, a
Phase 3 trial from 2021 involved participants receiving three MDMA doses over an 18-week
period along with manualized therapy, with significant improvement compared to placebo: over
67% of participants no longer met the diagnostic threshold for PTSD across a broad range of
symptoms, compared to 32% in the placebo group [@mitchelletal_2021_mdmaassisted]. Additional evidence
suggests that a considerable proportion of self-reported substance users support MDMA research
(68.1%), believe in the potential of MDMA-assisted therapy to help with alcohol and drug abuse
Chemical Conversations 2 disorders and it’s common comorbidity, PTSD (70.1%) and would be willing to participate if eligible (58.8%), across diverse racial and ethnic groups— a previous concern in the context of
equitable distribution of MDMA-assisted therapy, given the disproportionate extent to which
substance abuse (and it’s comorbidities) affect minorities [@jones_2023_perspectives].
Even with these advances, the road to MDMA-AT's broad approval and adoption is long
and complex. This is due to several concerns in the community, such as the potential for abuse
and the investment required to train therapists with proper protocols [@maderoalvarez_2023_premise].
Additionally, there is a concern that persistent use of MDMA could lead to decreased cognitive
function, which is a significant argument against MDMA-AT [@wagneretal_2015_learning]. A gaping
issue here is that it is almost impossible to construct a double-blind between placebo and MDMA
conditions, given the obvious external effects of MDMA, which could impact the results. This
exact rationale was behind the recent rejection of MDMA as a form or aid of treatment
[@kupferschmidt_2024_fda]. There are definite methodological advances that need to be put in place
which accurately weight the risk and benefits of such therapeutic treatments including
appropriate training and preparation for both the therapist and the individual receiving MDMA.
Wider application for such methods will require research and analysis that cover current gaps
about our knowledge of MDMA and the experience it induces, especially in a clinical setting
with a practitioner.

## Research Gap and Thesis formation
One such analysis of interest is observing and understanding overt behavioral changes
under MDMA influence, more specifically linguistic implications, to potentially inform the
construction of a therapeutic aid. Since a critical part of PTSD therapy, like most others, involves
discussing traumatic experiences and articulating emotions, understanding MDMA’s effects on
speech could deepen our knowledge of its impact beyond general emotional facilitation.
Understanding these changes could help practitioners facilitate individuals who find it difficult to
connect with or express emotions effectively in clinical settings.
Some insights on this topic can be found in a study by @baggottetal_2015_intimate, which
demonstrated that MDMA alters speech content, particularly by increasing the use of social and
emotional words during discussions about intimate relationships. The study found that MDMA
enhances both positive and negative emotional language, using a software that assesses semantic
content, the LIWC (Linguistic Inquiry and Word Count) software [@chungpennebaker_2018_what]
potentially helping patients in therapy communicate complex emotions more effectively. These
findings align with anecdotal reports of MDMA encouraging emotional disclosure and suggest
that MDMA may help patients develop a language of emotional insight essential for successful
trauma processing in therapy [@baggottetal_2015_intimate].
Further knowledge into MDMA’s effects on speech are provided in a study by @marroneetal_2010_amphetamine, which compared MDMA (dose) and methamphetamine (dose) on verbal fluency
and coherence. This within-participant study showed that while methamphetamine increased
speech fluency (ability to accurately string words together) and coherence (logical and
consistent), MDMA tended to decrease fluency and impacted participants' self-rated
concentration. Movie descriptions following MDMA were self-rated as less coherent than those
after methamphetamine, suggesting that MDMA’s effects on language may differ significantly
from other amphetamines.
While these studies examined MDMA's effects on linguistic fluency and emotional
language in addition to scraping the surface with authenticity, they did so in a setting with no
direct interaction with the participant. This thesis proposes an added variable of familiarity and
unfamiliarity to an individual in the know of the procedure, known as the confederate. Including
this variable provides a novel perspective on the research of MDMA, it may help decipher if
presence and interaction with an individual (or practitioner) can encourage the participant even
further to elucidate their emotional state. This addition may not only help measure the viability
of the therapeutic procedure but also inform policies and training for it. Questions of the additive
nature of both MDMA and familiarity to the individual are pertinent here.

## Research Questions and Hypotheses
This thesis primarily aims to identify linguistic markers of authenticity and emotionality
under the influence of MDMA to understand the extent of MDMA-assisted therapy (MDMA-
AT) in in addition to the modulating effects of partner familiarity.
To effectively examine these aims, it is essential to first define and contextualize the primary
concepts relevant to this study: Authenticity and Emotionality. Authenticity refers to the degree
to which an individual is monitoring their speech (LIWC — LIWC Analysis, n.d.), while
emotionality is more about the actual words spoken and their score within LIWC.

I hypothesize that MDMA will increase linguistic markers of authenticity and
emotionality compared to placebo [@baggottetal_2015_intimate; @mollaetal_2023_druginduced] I expect to seehigher authenticity and emotionality markers in conversations with familiar partners. Familiarity
can create a sense of comfort, making speech more natural and spontaneous (LIWC — LIWC
Analysis, n.d.). On the other hand, when interacting with an unfamiliar partner, individuals may
be more cautious about how they present themselves, leading to my hypothesis of a decrease in
authenticity and emotionality markers as they self-monitor their language more closely.

# Methods
This thesis project presents a secondary analysis of data from a clinical MDMA study
performed at the Human Behavioral Pharmacology Lab by P.I. Harriet de Wit, post-doc Hanna
Molla and other members of the Lab.

## Ethical Approval
This study was approved by the University of Chicago. All participants provided
informed consent to participate and were given a 250 dollars incentive after all sessions and 50 dollars if theydropped out before completion.

## Participants
Healthy male and non-pregnant female healthy adults, aged 18 to 35, were
recruited through posters, print and internet advertisements, and word-of-mouth referrals (n=45, f = 20; 44.5% and m= 25; 55.5%). Eligible candidates were those who reported prior psychedelic
use (1-40 occasions) and demonstrated verbal fluency in English. All participants passed
comprehensive medical and psychiatric screenings, including a structured clinical interview,
SCL-90R assessment, electrocardiogram, and physical examination. Major exclusion mental and
physical criteria include previous treatment for drug or alcohol problems or current substance
dependence [@americanpsychiatricassociation_2013_diagnostic]; past year panic disorder, history of psychotic or manic episodes [@americanpsychiatricassociation_2013_diagnostic]; cardiovascular illness or high bloodpressure, abnormal EKG, and pregnancy or lactation (females).

## Procedure
Participants engaged in four laboratory sessions, conducted in random order: Receive
MDMA (100 mg) and engage in a conversation with an Unfamiliar partner (MU), Receive
placebo and engage in a conversation with an Unfamiliar partner (PU), Receive MDMA (100
mg) and engage in a conversation with a Familiar partner (MF), and Receive placebo and engage
in a conversation with a Familiar partner (PF).

The partners were strangers before each session, but before participants received drug,
familiarity was established with two of the partners with a bonding conversation procedure
[@aronetal_1992_inclusion; @aronetal_1997_experimental]. One hour before ingesting the drug or placebo,
participants either engaged in a 45-min conversation to establish familiarity with a partner
(familiar sessions), or they spent time in a room without talking (Unfamiliar sessions).

On each session, baseline measures of heart rate, blood pressure, and oxytocin (plasma
sample were collected) were obtained, and participants were tested for recent drug use and
pregnancy. Then the participants spent 45 minutes in the same room as their partners with or
without social interaction and filled out surveys. Following this they ingested MDMA (100 mg)
or a placebo capsule, under a double-blind condition. Subjective measures were taken at every
30-minute mark. At the peak drug effect (60 minutes), the confederate joined the participant for a 15-minute test conversation (which was audio recorded), this conversation was about an
important person in the participant’s life which they had already listed at the orientation. At the end of this conversation and then the entire session, additional plasma samples were collected. At the 240-minute mark, the participant was provided with a snack and allowed to leave at the
experimenter’s discretion.

## Data Cleaning and Outcome Measures
The main source of data in this project are the audio recordings obtained through test
conversations. These will be transcribed into text files using Happy Scribe and human review,
with dialogues from the confederate removed. This clean text will be run through Linguistic
Inquiry and Word Count (LIWC), which is designed to count words associated with specific
psychological and grammatical dimensions to provide quantitative data [@chungpennebaker_2018_what].

For perceived authenticity, LIWC's developers categorized it as the degree to which an
individual self-monitors their speech. While high authenticity scores can be observed in
impromptu conversations between friends, prewritten speeches tend to score lower (LIWC —
LIWC Analysis, n.d.). This measure has been utilized by [@markowitzetal_2023_authentic] in studying the social benefits of authentic speech.

For emotional content (emotionality), LIWC analyzes both positive and negative
emotional expressions through specific word categories. Positive emotions are tracked through
words like "good" and "love," while negative emotions are identified through terms such as
"bad" and "hurt." The analysis further breaks down negative emotions into specific states,
including anxiety (measured through words like "worry" and "nervous"), anger (identified by
terms such as "mad" and "angry"), and sadness (tracked through words like "cry" and
"disappoint").

#Results

Prior to running a multiple regression model on the data, novel variables are to be defined and categorized

```{r load-data, include=FALSE}
# Import data from CSV
df <- read_csv("ChemicalConversationsdata.csv")

# Preview data
glimpse(df)
```

```{r data tranformation, include=FALSE}
df <- df %>%
  mutate(
    across(c(emotion, Authenticity, emo_pos, emo_neg, emo_anx, emo_anger, emo_sad, focuspast, focuspresent, focusfuture), as.numeric),
    across(c(Drugcondition, Familiarity, Filename, SubjectID, SessionCondition), as.factor)
  )

#Verify results
head(df)
```

```{r mixed-models}
#| echo: true

# Fit the mixed-effects models
mlfit1 <- lme(Authenticity ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit2 <- lme(emotion ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit3 <- lme(emo_pos ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit4 <- lme(emo_neg ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit5 <- lme(emo_anx ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit6 <- lme(emo_anger ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit7 <- lme(emo_sad ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit8 <- lme(focuspast ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit9 <- lme(focuspresent ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")
mlfit10 <- lme(focusfuture ~ Familiarity * Drugcondition , random =  ~ 1 | SubjectID, data = df, method = "ML")

# Summarize the models
summary(mlfit1)
summary(mlfit2)
summary(mlfit3)
summary(mlfit4)
summary(mlfit5)
summary(mlfit6)
summary(mlfit7)
summary(mlfit8)
summary(mlfit9)
summary(mlfit10)
```


